---
title: "Venn Diagrams"
output: html_notebook
---

#read in plx vx plx + corin RNA-seq files
```{r}
rna_451 <- read.csv("/Users/rjfisher/Library/Mobile Documents/com~apple~CloudDocs/BUSM/Alani Lab/DATA/Muzhou_RNAseq_Data_Analysis/RNAseq/plx_plxcorin_451.csv")
rna_1205 <- read.csv("/Users/rjfisher/Library/Mobile Documents/com~apple~CloudDocs/BUSM/Alani Lab/DATA/Muzhou_RNAseq_Data_Analysis/RNAseq/plx_plxcorin_1205.csv")
```

```{r}
rna_451$padj[rna_451$padj == "0"] <- "1.00e-306"
rna_1205$padj[rna_1205$padj == "0"] <- "1.00e-306"

rna_451$padj <- as.numeric (rna_451$padj)
rna_1205$padj <- as.numeric (rna_1205$padj)

rna_451$padj <- -log10(rna_451$padj)
rna_1205$padj <- -log10(rna_1205$padj)
```

#FC > |2|, padj < 0.01
```{r}
rna_451_sig_up <- rna_451 %>% filter(FC > 2 & padj > 2)
rna_1205_sig_up <- rna_1205 %>% filter(FC > 2 & padj > 2)

rna_451_sig_down <- rna_451 %>% filter(FC < -2 & padj > 2)
rna_1205_sig_down <- rna_1205 %>% filter(FC < -2 & padj > 2)
```

```{r}
library(eulerr)
library(ggVennDiagram)
```

#up genes
```{r}
rna_451_sig_up_gene <- rna_451_sig_up$gene
rna_1205_sig_up_gene <- rna_1205_sig_up$gene

# Create a list of sets
sets_up_list <- list(
  rna_451_sig_up_genes = rna_451_sig_up_gene,
  rna_1205_sig_up_genes = rna_1205_sig_up_gene
)

ggVennDiagram(sets_up_list)
```

#down genes
```{r}
rna_451_sig_down_gene <- rna_451_sig_down$gene
rna_1205_sig_down_gene <- rna_1205_sig_down$gene

# Create a list of sets
sets_down_list <- list(
  rna_451_sig_down_genes = rna_451_sig_down_gene,
  rna_1205_sig_down_genes = rna_1205_sig_down_gene
)

ggVennDiagram(sets_down_list)
```
